R Notebook

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.15.22

# Network: Creating network Data
```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}

colnames(smugCovIdx )

@@

# Network Info
  Network Objects: EDGE LIST
                  STATNET: smugEL_sn
                  IGRAPH: smugEL_ig

## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
```{r Network: Identify critical features, echo=FALSE}

#**Statnet EdgeList**   smugEL_sn
#####

@@

```{r STATNET: Network Description}

      # class of an object
class(smugEL_sn )

      # list the structure of smugCovIdx
str(smugEL_sn )

      ## Network Attributes
 print(smugEL_sn)
          # Vertices =  
          # Directed = 
          # hyper = 
          # loops = 
          # multiple = 
          # bipartite = 
          # total edges = 
                # missing edges =
                # non-missing edges = 
          # Vertex attribute names:
          # Edge Attribute Names: 
```

```{r igraph: Network Description, echo=TRUE}

      # class of an object
    class(smugEL_ig )

        # list the structure of smugCovIdx
    str(smugEL_ig )

## Network Size
      # Count Vertices
    vcount(smugEL_ig)

@@

## Network Mode
    # Bipartitie / Unimodal
    is_bipartite(smugEL_ig)

## Edges    
    # Un/directed 
    is_directed(smugEL_ig)

    # weighted or unweighted?
    is_weighted(smugEL_ig)

@@

Classifies all triads in the network. The triad
census provides a fundamental descriptive insight
into the types of triads found in a particular
smugEL_

>>>>

# Network: Creating network Data
```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
colnames(smugCovIdx )

@@

# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}

#**Statnet EdgeList**   smugEL_sn
#####
#### class of an object
class(smugEL_sn )
class(smugEL_ig )

# list the structure of smugCovIdx
str(smugEL_sn )
str(smugEL_ig )

@@

## EDGELIST: Describe

```{r igraph: Network Description, echo=TRUE}
# class of an object

    class(smugEL_ig )

# list the structure of smugCovIdx

    str(smugEL_ig )
#     Count Vertices
    vcount(smugEL_ig)

@@

# Is this a Bipartite or single mode network?
    is_bipartite(smugEL_ig)

#  Are edges directed or undirected?
    is_directed(smugEL_ig)

#Are edges weighted or unweighted?
    is_weighted(smugEL_ig)

@@

Classifies all triads in the network. The triad
census provides a fundamental descriptive insight
into the types of triads found in a particular
dataset.
